Done

### 2025-01-06 done.qmd
update

@@

>>>>

2024-12-19: Kate took this picture in [Elm](https://www.elmsheffield.co.uk/)

<a href="images/tom_2024-12-19.jpg"><img src="images/tom_2024-12-19small.jpg" height = 400></a>

@@

2012-06-06: [Fundamentals of learning: the exploration-exploitation trade-off](done/2012-06-12.html)

2012-06-04: [New paper: A novel task for the investigation of action acquisition](done/2012-06-12.html)
